---
title: "425 FINAL"
author: "Chengyan Ji"
date: "2021/11/18"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("readxl")
library("readxl")
```

## R Markdown

# The file is corrupted so I downloaded the readxl package.

```{r}
df = read_excel("C:/Users/kurtji/Desktop/STAT425/FINAL/Real_estate_valuation_data_set.xlsx")
colnames(df) <- c("Index", "X1_transaction_date", "X3_house_age", "X4_distance_to_the_nearest_MRT_station", "X5_number_of_convenience_stores", "X6_latitude", "X7_longitude", "Y_house_price_of_unit_area")
```

# Define the function to extract month and year from date
```{r, echo=FALSE}
transferData <- function(num) {
  month = as.character(round((num %% 1) * 12))
  #print(month)
  if (month == '0') {
    month = '12'
    year = as.character(floor(num) - 1)
  } else {
    year = as.character(floor(num))
  }
  #print(year)
  date = paste(year , '-', month, '-01', sep = (''))
  #print(date)
  #return('hi')
  return(as.Date(date))
}
```

# Modify data structure
```{r}
list <- do.call("c", lapply(df$X1_transaction_date, transferData))
df1 = df
df1$X1_transaction_date_1 <- list
df1$X1_transaction_year <- format(as.Date(df1$X1_transaction_date_1, format="%d/%m/%Y"),"%Y")
df1$X2_transaction_month <- format(as.Date(df1$X1_transaction_date_1, format="%d/%m/%Y"),"%m")

#df1 <- df1[,-1]
df1 <- df1[c("Y_house_price_of_unit_area", "X1_transaction_date", "X1_transaction_year", "X2_transaction_month", "X3_house_age", "X4_distance_to_the_nearest_MRT_station", "X5_number_of_convenience_stores", "X6_latitude", "X7_longitude")]
```

# Output the dataset
```{r}
write.csv(df1,"C:/Users/kurtji/Desktop/STAT425/FINAL/Real_estate_valuation_data_set_1.csv", row.names = TRUE)
```

# Split with 3-7 ratio
```{r}
train_index <- sample(1:nrow(df1), 138, replace = FALSE)
train_data <- df1[train_index,]
test_data <- df1[-train_index,]
```

# Output the dataset
```{r}
write.csv(train_data,"C:/Users/kurtji/Desktop/STAT425/FINAL/Real_estate_valuation_data_set_1_train.csv", row.names = TRUE)
write.csv(test_data,"C:/Users/kurtji/Desktop/STAT425/FINAL/Real_estate_valuation_data_set_1_test.csv", row.names = TRUE)
```

## Exploratory Analysis
```{r}
summary(df1)
```
# Include some box plots
```{r}
library(ggplot2)
```

```{r}
ggplot(df1, aes(x = X2_transaction_month, y = Y_house_price_of_unit_area)) +
  geom_boxplot(fill = "#4271AE", colour = "#1F3552", alpha = 0.8) + 
  scale_x_discrete(name = "Month of Purchase") +
  scale_y_continuous(name = "House Price per Unit Area", breaks = seq(0, 125, 20)) + 
  ggtitle("Boxplot of house price by month")
```

# House price against laltitude and altitude (scatter)

```{r}
ggplot(df1, aes(x = X4_distance_to_the_nearest_MRT_station, y = Y_house_price_of_unit_area)) +
  geom_point(fill = "#4271AE", colour = "#1F3552", alpha = 0.8) + 
  scale_x_discrete(name = "distance to nearest MRT station") +
  scale_y_continuous(name = "House Price per Unit Area", breaks = seq(0, 125, 20)) + 
  ggtitle("Scatterplot of house price over distance to nearest MRT station") +
  geom_smooth(method = "lm", se = TRUE)
```

# Histograms

```{r}
hist(df1$X3_house_age, breaks = 50, col=rgb(1,0,0,0.5), xlab="house age", 
     ylab="frequency", main="distribution of house age" )
```

# Model Diagnostic(To get clean data, but the project eventually used original data)

```{r}
#Finding high leverage points
dim(df1)
n = 414
p = 6
fit_1 <- lm(Y_house_price_of_unit_area ~ ., data = df1)
lev = influence(fit_1)$hat
lev[lev >= 2*p/n]
which(lev >= 2*p/n)
#drop the high leverage points
df2 = df1[-which(lev >= 2*p/n),]
```
```{r}
#Finding outliers
jack = rstudent(fit_1)
qt(.05/(2*n), 414)

sort(abs(jack), decreasing = TRUE)[1:5]

#there are two outliers
#dropping outliers
df3 = df2[-c(271,114),]
```
```{r}
#Finding highly influential points
cook = cooks.distance(fit_1)
max(cook)
#max is 0.1949, no greater than 1

#this function is not working
#halfnorm(cook, labs = row.names(df), ylab = "Cook's distance")
```

